I would first thank Emery Berger, my Ph.D. thesis advisor, for his wonderful supervision and enthusiastic support in the development of this thesis work. He has been very generous and understandable to my family issues. Besides, Emery taught me to work on those important practical projects and take everything seriously. I hope that I could be as lively, enthusiastic, and energetic as Emery in one day to my students.  I also thank my dissertation committee: Scott Kaplan, Yuriy Brun, and Israel Koren, for their valuable insights, feedback, and support. 

I am also fortunate to work with Chen Tian, Timothy Richards, Ziang Hu, Daniel Waddington, Seetharami Seelam, Wei Tan, Liana Fong, Arun Iyengar, and Prashant Shenoy. They provide me valuable guidance and suggestions on those projects we worked together. I also thank Leeanne Leclerc, James Allan, and Laurie Downey for their help to make my experience at UMass go as smoothly as possible. 

I couldn't finish my thesis without the help of PLASMA  labmates, including Charlie Curtsinger, Ting Yang, Gene Nowark, Kaituo Li, John Altidor, Divya Krishnan, Dan Barowy, Dimitar Gochev, John Vilk, Nitin Gupta, Justin Aquadro, and Emma Tosch. I also feel lucky to meet many friends in the computer science department, including Ming Li, Tingxin Yan, Zongfang Lin, Kun Tu, Xiaozhen Tie, Fangyuan Zhou, Hong Zhang, Xiaojian Wu, Pengyu Zhang, Yue Wang, Wenzhao Liu, etc. I will never forget your help in my life. 

Finally, I would give my special thanks for my wife, Yuyu Tang. She quitted her job to support my crazy idea of getting a Ph.D. degree. She also took care of most of household duties and spent much of her time to take care of our two adorable kids, Yanbin Liu (Grace) and Yanlin Liu (Eileen). My buddy, Guangming Zeng, also deserves my special thanks for his generous help and valuable discussion when I chose the career in the computer science field. I also want to thank for my kids, my passed grandma, my parents, sisters, and brothers for their understanding and support.    

