% Dynamic analysis
% Super awesome

Dynamic analysis tools are widely used to find bugs in
applications. They are popular among programmers because of their
precision---for many analyses, they report no false positives---and
can pinpoint the exact location of errors, down to the individual line
of code.

Perhaps the most prominent and widely used dynamic analysis tool for
C/C++ binaries is Valgrind~\cite{overflow:valgrind}. Valgrind's most
popular use case, via its default tool, memcheck, is to check memory
errors, including buffer overflows, dangling pointer errors, and
memory leaks.

Unfortunately, while these dynamic analysis tools are useful, they are
often expensive. Using Valgrind typically slows down applications by
10-100$\times$. Faster dynamic analysis frameworks exist for finding
particular errors, but all impose substantial overheads. Google's
AddressSanitizer, for example, detects buffer overflows and
use-after-free errors, but slows applications by around 30\%. Precise
memory leak detectors that identify the point at which objects are
leaked remain far more expensive.

Because of their overhead, dynamic analysis tools are only used during
debugging. However, they are limited by definition to the executions
that they have seen. The fact that using these tools in deployed
applications is not practical means that errors that could
have been found trivially instead require painstaking debugging
later.

This paper presents a new approach that enables extremely lightweight
dynamic analysis for an important class of errors. These errors share
a monotonicity property: when an error happens, evidence that it
happened either remains or grows so that it can be recovered at a
later point. When this evidence is not naturally occurring, it is
often possible to ``plant'' evidence via what we call \emph{tripwires}
to ensure later detection. An example tripwire is a random value (also
known as a ``canary'') placed in unallocated space between heap
objects. A corrupted canary is incontrovertible evidence that a buffer
overflow occurred at some time in the past.

We present a system called \doubletake{} that is based on the
following key insight: by combining checkpointing with evidence
gathering, it is possible to let applications run at full speed in the
common case (no errors). If we discover evidence of an error, we can
go back and re-execute the program with instrumentation activated to
find the exact cause of the error.

\doubletake{} performs its checkpoints only at
irrevocable system calls, amortizing the cost of checkpoint
collection. Each checkpoint saves the contents of the stack,
globals, registers, and the heap. If it finds evidence of an error at
the next system call or after a segmentation violation, \doubletake{}
re-executes the application from the most recent checkpoint. During
re-execution, it triggers instrumentation to let it precisely locate
the source of the error. For the buffer overflow
example, \doubletake{} sets hardware watchpoints on the tripwire
memory locations that were found to be corrupted. During re-execution,
the program then halts at exactly the point where the buffer overflow
occurred.

We implement \doubletake{} as a drop-in library that can either be
linked directly with the application under analysis, or which can be
activated by setting an environment variable (\texttt{LD\_PRELOAD} on
Unix systems) to dynamically load \doubletake{} before execution. No
re-compilation or availability of source code is required. This
approach makes \doubletake{} as convenient to use as Valgrind.

We have built three different analyses using \doubletake{}: buffer
overflow detection, dangling pointer (use-after-free) detection, and
memory leak detection. All of these analyses run without any false
positives, halt execution at exactly the point that the error occurs,
and operate with extremely low overhead. For example, \doubletake{}'s
buffer overflow analysis operates with just 5\% overhead on average.

%\subsection{Outline}
%This paper talks about those related works in next section. Section 3 discusses specific mechanisms 
%used by \doubletake{}. Section 4 describes some implementation details worth noting. 
%Section 5 evaluates the performance and effectiveness of \doubletake{} and Section 6
%discusses some problems and extending possibilities of \doubletake{}.
%Section 7 concludes this paper. 
